Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles: Supplementary information (S1)

### 2021-05-10 source/tex/ladybug_adhesion.tex
finalized manuscript based on thomas's suggestions
ready to send to JEB

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\SectionNumbersOn
%\setkeys{acs}{doi = true}
\setkeys{Gin}{width=\linewidth}
\usepackage{subcaption}

@@

While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much more rare and has been relatively unexplored. Some aquatic insects like diving beetles \cite{Chen:2014} or midge larva \cite{Kang:2020} use suction cups to adhere to surfaces. However, underwater adhesion mediated by secreted liquids require the displacement of the water at the interface first and a spreading of the fluid on the substrate. One relatively simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \cite{Seymour:2013}. This has been shown in a recent study by \citet{RN87} that that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach quite well to surfaces underwater by using such an air bubble. Their naturally hydrophobic tarsal hairs trap the bubble around the pads when being submerged underwater, which de-wets the surface on contact. It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the de-wetted area results in its adhesion underwater. However, it remains unclear if an air bubble is necessary for adhesion and what, if any, contribution it has to the adhesive force. The oily tarsal adhesive fluid found in insects alone might be sufficient in creating the necessary capillary adhesion even without a bubble, given that the fluid remains on the hair tips when submerged. In ladybug beetles, the tip of each seta secretes approximately one femtoliter of tarsal adhesive fluid by each step \cite{RN108}. The fluid's chemical composition in green dock beetles was identified to be an oil-containing mixture of mostly long chain hydrocarbons\cite{RN96} with traces
of triglycerides, fatty acids and cholesterol in ladybirds \emph{Hemisphaerota cyanea} and \emph{Epilachna vingtipunctuata}\cite{RN221,RN222}, rendering it immiscible with water. %split references%

@@

\section{Experimental}
%normal to untrated glass%
Normal adhesion force measurements on a restrained leg in a live
beetle were performed. We focused our study only on a single tarsal adhesive pad of the leg by carefully immobilizing it (described later) to prevent any dynamic influence of its claws or other tarsomeres/legs, which might otherwise exist under the beetle's natural walking conditions, influencing its adhesion. 
We characterised adhesion by the pull-off force
during detachment, tested on smooth normal and
fluorinated glass surfaces representing hydrophilic and hydrophobic substrates
respectively. When no water was present, we labelled the mode of contact
as ``\emph{in air}''. Underwater, measurements
were done both in the presence and absence of a trapped air bubble (``\emph{underwater:
bubble}'' and ``\emph{underwater: no bubble}'', respectively) to
investigate the air bubble's role in underwater adhesion. Adhesion force
for each of the labelled contact modes were compared for both substrates.

@@

Five force measurements were subsequently performed, each on a fresh spot of the substrate, and averaged for data analysis. 
Experiments were repeated with five distinct male beetles for each combination of contact mode (``\emph{in air}'', ``\emph{underwater:
bubble}'' and ``\emph{underwater: no bubble}'') and substrate chemistry (hydrophilic and hydrophobic). Thus, in total, 30 distinct beetles were tested. After an experiment, the beetle was marked on its elytra and released back into the box to ensure the same beetle was not used for any subsequent adhesion tests.
%mention data points number clearly for each box, what is averaged etc. also%

@@

Data sets were compared for statistical differences using pairwise
Student t-test and their corresponding p-value and Common Language
Effect Size (CLES) are reported. Shapiro-Wilk test was done for each
data set to verify a normal distribution of its residuals and Levene's
test was done to check for variance homogeneity, to validate the t-test
assumptions. Bonferroni's correction was used to account for multiple
comparison between groups.
%Include ANOVA as well, include F, t, degrees of freedom%
\subsubsection{Substrate preparation}

Standard 20 mm wide glass cover-slips were used as the hydrophilic
substrate. Glass was wiped with isopropanol, rinsed in water and dried
under nitrogen flow before use. For the hydrophobic substrate, the glass cover slip was coated with
a fluorosilane via chemical vapour deposition (CVD). First, the glass
was cleaned using IPA. The surface was then plasma cleaned in an oxygen
plasma chamber (\emph{Femto, Diener Electronic GmbH, Germany}) for 10 min at 120 W. Next, 0.2 ml of
Trichloro(1H,1H,2H,2H-perfluorooctyl) silane (PFOTS), procured from
Sigma Aldrich, was put in a sealed chamber along with the the cleaned
glass. The chamber was placed under 100 mbar pressure for 10 min for
the CVD process. Finally, the substrate was annealed at 150\textcelsius{}
for 3 hours. Henceforth, we refer to the hydrophilic normal glass substrate 
as simply \emph{Glass} and the hydrophobic fluorinated glass substrate as \emph{PFOTS}.

@@

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing
 adhesion force measurements of ladybug beetle's (\emph{Coccinella
septempuctata}) distal pad on normal hydrophilic glass (blue) and hydrophobic PFOTS coated glass (red) substrates in air and underwater
conditions (n=30). The two modes of contact during underwater experiments
are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
and \textquotedblleft\emph{no bubble}\textquotedblright . Crosses
represent theoretical predictions (see text) of adhesion force, while, circles
represent the contribution of the bubble itself, calculated from the
capillary bridge model. In the model, hair diameter = 4 \textmu m,
pad diameter = 200 \textmu m, hair length = 40 \textmu m,
N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
= 4.2 fL and V\protect\textsubscript{bubble} = 1.2 nL. Interfacial
tension of the tarsal adhesive fluid in air and water were assumed to be
24 mN m\protect\textsuperscript{-1} and 48 mN m\protect\textsuperscript{-1} respectively and water surface tension is 72 mN m\protect\textsuperscript{-1}.}
\end{figure}
%outlier%
Apart from the three depicted contact modes, we observed an additional
fourth mode which occurred in roughly 25\% of our underwater experiments using degassed water.
In this scenario, the ventral view recordings show that none of the hairs
appear to contact well with either glass or PFOTS substrate (supplementary video S5), unlike the other
three contact modes (supplementary video S2-S4). This ``bad contact'' scenario only happened underwater and shows no adhesion 
with either glass or PFOTS substrate. While it was not completely
clear why such a contact occurs, there can be two possible reasons.
First, the hairs could get bundled due to a small air meniscus within
the hairs, resulting in their disorientation. Second, a thin water
layer at the substrate interface might not be drained out to allow
the hairs to make contact with the substrate, resulting in a loss
of adhesion.

@@

\begin{figure}[H]
\includegraphics{Figure-8-contact_angle_schematic}\caption{\label{fig:Oil-contact-images}Simulation snapshots of oil capillary
meniscus in contact with normal glass and PFOTS-coated glass in air and underwater conditions.
The corresponding interfacial tension, \textgreek{g}, and contact
angle, \ensuremath{\theta}, used to predict the ladybug's adhesion
are labelled for each case.}
\end{figure}

@@

Predictions of the ladybug's adhesion from the capillary bridge model
agree with our experimental results (Figure \ref{fig:Effect-of-contact}).
In underwater conditions without a trapped air bubble, adhesion to a hydrophobic
substrate is significantly larger than to a hydrophilic substrate.
This is explained by the different interfacial tension of the oily tarsal secretion and its contact
angles with the substrates in air and underwater, which determines
the capillary adhesive force in each case (Figure \ref{fig:Oil-contact-images}).
However, the experiments don't show the predicted $\sim$ 2.6 times
increase in underwater adhesion relative to that in air on the hydrophobic
PFOTS-coated surface. This discrepancy could be due to our assumptions of
the oily fluid's interfacial properties. If we choose $\gamma_{fa}$=30
mN m\protect\textsuperscript{-1} and $\gamma_{fw}$=40 mN m\protect\textsuperscript{-1}, the corresponding increase in adhesion
will be $\sim$ 1.7, closer to our experimental value of $\sim$ 1.
The resulting change in $\theta_{fa}$ and $\theta_{fw}$ will further
decrease this number. Direct measurement of the fluid's interfacial
properties is thus essential to better predict the insect's adhesion,
and will be a subject of future studies. Further, due to surface inhomogeneities,
not all the hairs might be able to completely drain the interfacial
water layer, in order for the tarsal adhesive fluid to make a direct contact
with the substrate. This can further reduce underwater adhesion, in
comparison to our theoretical predictions which assumes a perfect
contact of all hairs' terminals.
%FDMS keep as unpublished data, remove from supplementary.%
In the model, we assume that all the hairs detach simultaneously to
give a theoretical maximum achievable adhesion force. In our experiments,
however, not all hairs make a perfect contact with the substrate despite our 
best efforts to align the pad parallel to the surface. Furthermore, during detachment, 
the constrained pad typically peels off from its proximal to distal end rather
than detach simultaneously. Our model also assumes the hairs to be
of similar geometry, unlike the male beetle's pad which has a distribution
of flat or pointed tipped hairs. Thus, it's not surprising that the
model overestimates the adhesion forces. The predictions are however
in the same order of magnitude as experiments, and the qualitative
trend is consistent for both hydrophilic and hydrophobic substrates
in air and underwater.

Our study provides further validation that capillary forces govern the ladybug's adhesion and van der Waals contribution,
if any, must be negligible. Further, the capillary forces can even
enable ladybug attachment underwater depending on the substrate chemistry.
When underwater, without a trapped bubble, the pads adhere strongly
to a hydrophobic substrate, but poorly to a hydrophilic substrate,
even though it shows similarly strong adhesion to both substrates
in air. This effect can be explained by capillary forces and the wetting properties of the fluid. Our
preliminary chemical composition analysis of a beetle's tarsal secretions before and after immersing its leg underwater 
validates our assumption that the tarsal adhesive fluid should form capillary bridges with the substrate
underwater, instead of getting washed away (see supplementary info Section S1.5).

To some extent, the findings could be extended to other animals relying on oily
secretions for adhesion. For example, ants are known to possess smooth adhesive pads which secrete a fluid containing oily substances \cite{RN201}.
It has been reported that some ants show similar adhesion on hydrophobic substrates under wet and dry conditions \cite{RN213},
similar to what we see in a ladybug. This observation can again be explained by a capillary model as before. Recent experiments on
geckos revealed that they can attach well to fluoropolymer substrates (such as PTFE)
underwater while they show little adhesion to the same substrate in
air\cite{RN199,RN15}. Geckos are thought to rely on van der Waals
forces via dry contact with the substrate \cite{RN202}, although
recent observations of phospholipid footprints left behind walking
geckos \cite{RN205} could change that picture. Since geckos adhere
poorly to PTFE (surface energy $\sim$ 20 mN m\protect\textsuperscript{-1}) one can
speculate that the phospholipid material has a higher surface energy,
and consequently makes a higher contact angle with PTFE in air. Let
us assume the phosopholipid substance to be a fluid similar to oil 
with $\gamma_{fa}$= 30 mN m\protect\textsuperscript{-1} and $\gamma_{fw}$= 42 mN m\protect\textsuperscript{-1} such that
its contact angle with PTFE is 80\textdegree . Equation \ref{eq:theta_fw}
then gives us an underwater contact angle of 70\textdegree{} for the
phospholipid fluid. Thus, on a PTFE surface, the capillary bridge
model can predict a higher adhesion underwater than in air due to
its lower contact angle and higher interfacial energy underwater.
Based on similar assumptions, we predict the net adhesion force for
the gecko on different substrates (Figure \ref{fig:Comparison-with-model}).
The adhesion force predictions are in good qualitative agreement with
the whole animal experimental shear force values reported for the
gecko, with the trend of higher adhesion in air than underwater for
glass, similar adhesion in air and underwater for PMMA/OTS-SAM and
lower adhesion in air than underwater for PTFE. We, thus, propose
that the underwater experiments performed on geckos \cite{RN199,RN15}
indicate a capillary contribution to gecko adhesion. Previous studies on gecko adhesion have attributed capillary effects to be a result of
water condensation from ambient humid air onto the setal hair tips \cite{RN197, RN203, RN218}.
We however emphasize that capillary contribution in gecko adhesion could rather be a result of its setal phospholipid layer rather than water. %SURFACE TENSION SOURCE%
The previously reported influence of humidity on gecko adhesion \cite{RN197} could possibly be an effect of change in surface tension of the oily phospholipid layer at different humidity, which will in-turn influence the capillary adhesion force. We suggest performing single seta adhesion force tests similar to \citet{RN202}
using a hydrophilic and fluorinated probe in air and underwater conditions. 
If the fluorinated probe shows higher adhesion underwater than in air on a single seta, this
would confirm the role of capillary contributions due to an oil-like phospholipid layer to gecko adhesion. Further work is also necessary to validate if the phospholipid layer in geckos' toes indeed has fluid-like properties.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\SectionNumbersOn
%\setkeys{acs}{doi = true}
\setkeys{Gin}{width=\linewidth}
\usepackage{subcaption}
\usepackage[pagewise]{lineno}
\linenumbers

@@

While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much rarer and has been relatively unexplored. Some aquatic insects like diving beetles \cite{Chen:2014} or midge larva \cite{Kang:2020} use suction cups to adhere to surfaces. However, underwater adhesion mediated by secreted liquids require the displacement of the water at the interface first and a spreading of the fluid on the substrate. One relatively simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \cite{Seymour:2013}. This has been shown in a recent study by \citet{RN87} that that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach quite well to surfaces underwater by using such an air bubble. Their naturally hydrophobic tarsal hairs trap the bubble around the pads when being submerged underwater, which de-wets the surface on contact. It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the de-wetted area results in its adhesion underwater. However, it remained unclear if an air bubble is necessary for adhesion and what, if any, contribution it has to the adhesive force. The oily tarsal adhesive fluid found in insects alone might be sufficient in creating the necessary capillary adhesion even without a bubble, given that the fluid remains on the hair tips when submerged. In ladybug beetles, the tip of each seta secretes approximately one femtoliter of tarsal adhesive fluid by each step \cite{RN108}. The fluid's chemical composition in green dock beetles was identified to be an oil-containing mixture of mostly long chain hydrocarbons\cite{RN96} with traces
of triglycerides, fatty acids and cholesterol in ladybirds \emph{Hemisphaerota cyanea} \cite{RN221} and \emph{Epilachna vingtipunctuata} \cite{RN222}, rendering it immiscible with water.

@@

\section{Experimental}

Normal adhesion force measurements on a restrained leg in a live
beetle were performed. We focused our study only on a single tarsal adhesive pad of the leg by carefully immobilizing it (described later) to prevent any dynamic influence of its claws or other tarsomeres/legs, which might otherwise exist under the beetle's natural walking conditions, influencing its adhesion. 
We characterised adhesion by the pull-off force
during detachment, tested on smooth untreated and
fluorinated glass surfaces representing hydrophilic and hydrophobic substrates
respectively. When no water was present, we labelled the mode of contact
as ``\emph{in air}''. Underwater, measurements
were done both in the presence and absence of a trapped air bubble (``\emph{underwater:
bubble}'' and ``\emph{underwater: no bubble}'', respectively) to
investigate the air bubble's role in underwater adhesion. Adhesion force
for each of the labelled contact modes were compared for both substrates.

@@

Five force measurements were subsequently performed, each on a fresh spot of the substrate, and were averaged to avoid pseudo-replication during data analysis. Experiments were repeated with 30 distinct male beetles for all combinations of contact mode (``\emph{in air}'', ``\emph{underwater:
bubble}'' and ``\emph{underwater: no bubble}'') and substrate chemistry (hydrophilic and hydrophobic), 5 beetles for each  combination. After an experiment, the beetle was marked on its elytra and released back into the box to ensure the same beetle was not used for any subsequent adhesion tests.

@@

Data sets were compared for statistical differences using two-way ANOVA analysis, with \emph{contact mode} and \emph{substrate chemistry} as the categorical variables and \emph{adhesion force} as the dependant variable. Pairwise
Student t-test were done for post-hoc analysis and their corresponding p-value and Common Language
Effect Size (CLES) are reported. Shapiro-Wilk test was done for each
data set to verify a normal distribution of its residuals and Levene's
test was done to check for variance homogeneity, to validate the t-test
assumptions. Bonferroni's correction was used to account for multiple
comparison between groups.

\subsubsection{Substrate preparation}

Standard 20 mm wide glass cover-slips were used as the hydrophilic
substrate. Glass was wiped with isopropanol, rinsed in water and dried
under nitrogen flow before use. For the hydrophobic substrate, the glass cover slip was coated with
a fluorosilane via chemical vapour deposition (CVD). First, the glass
was cleaned using IPA. The surface was then plasma cleaned in an oxygen
plasma chamber (\emph{Femto, Diener Electronic GmbH, Germany}) for 10 min at 120 W. Next, 0.2 ml of
Trichloro(1H,1H,2H,2H-perfluorooctyl) silane (PFOTS), procured from
Sigma Aldrich, was put in a sealed chamber along with the the cleaned
glass. The chamber was placed under 100 mbar pressure for 10 min for
the CVD process. Finally, the substrate was annealed at 150\textcelsius{}
for 3 hours. Henceforth, we refer to the hydrophilic untreated glass substrate 
as simply \emph{Glass} and the hydrophobic fluorinated glass substrate as \emph{PFOTS}.

@@

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing
 adhesion force measurements of ladybug beetle's (\emph{Coccinella
septempuctata}) distal pad on untreated hydrophilic glass (blue) and hydrophobic PFOTS coated glass (red) substrates in air and underwater
conditions (n=5 per box). The two modes of contact during underwater experiments
are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
and \textquotedblleft\emph{no bubble}\textquotedblright . The small diamonds represent outlier points. Crosses
represent theoretical predictions (see text) of adhesion force, while, circles
represent the contribution of the bubble itself, calculated from the
capillary bridge model. In the model, hair diameter = 4 \textmu m,
pad diameter = 200 \textmu m, hair length = 40 \textmu m,
N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
= 4.2 fL and V\protect\textsubscript{bubble} = 1.2 nL. Interfacial
tension of the tarsal adhesive fluid in air and water were assumed to be
24 mN m\protect\textsuperscript{-1} and 48 mN m\protect\textsuperscript{-1} respectively and water surface tension is 72 mN m\protect\textsuperscript{-1}.}
\end{figure}

Apart from the three depicted contact modes, we observed an additional
fourth mode which occurred in roughly 25\% of our underwater experiments using degassed water.
In this scenario, the ventral view recordings show that none of the hairs
appear to contact well with either glass or PFOTS substrate (supplementary video S3), unlike the other
three contact modes (supplementary video S2). This ``bad contact'' scenario only happened underwater and shows no adhesion 
with either glass or PFOTS substrate. While it was not completely
clear why such a contact occurs, there can be two possible reasons.
First, the hairs could get bundled due to a small air meniscus within
the hairs, resulting in their disorientation. Second, a thin water
layer at the substrate interface might not be drained out to allow
the hairs to make contact with the substrate, resulting in a loss
of adhesion.

@@

\begin{figure}[H]
\includegraphics{Figure-8-contact_angle_schematic}\caption{\label{fig:Oil-contact-images}Simulation snapshots of oil capillary
meniscus in contact with untreated glass and PFOTS-coated glass in air and underwater conditions.
The corresponding interfacial tension, \textgreek{g}, and contact
angle, \ensuremath{\theta}, used to predict the ladybug's adhesion
are labelled for each case.}
\end{figure}

@@

Predictions of the ladybug's adhesion from the capillary bridge model
agree with our experimental results (Figure \ref{fig:Effect-of-contact}).
In underwater conditions without a trapped air bubble, adhesion to a hydrophobic
substrate is significantly larger than to a hydrophilic substrate.
This is explained by the different interfacial tension of the oily tarsal secretion and its contact
angles with the substrates in air and underwater, which determines
the capillary adhesive force in each case (Figure \ref{fig:Oil-contact-images}).
However, the experiments don't show the predicted $\sim$ 2.6 times
increase in underwater adhesion relative to that in air on the hydrophobic
PFOTS-coated surface. This discrepancy could be due to our assumptions of
the oily fluid's interfacial properties. If we choose $\gamma_{fa}$=30
mN m\protect\textsuperscript{-1} and $\gamma_{fw}$=40 mN m\protect\textsuperscript{-1}, the corresponding increase in adhesion
will be $\sim$ 1.7, closer to our experimental value of $\sim$ 1.
The resulting change in $\theta_{fa}$ and $\theta_{fw}$ will further
decrease this number. Direct measurement of the fluid's interfacial
properties is thus essential to better predict the insect's adhesion,
and will be a subject of future studies. Further, due to surface inhomogeneities,
not all the hairs might be able to completely drain the interfacial
water layer, in order for the tarsal adhesive fluid to make a direct contact
with the substrate. This can further reduce underwater adhesion, in
comparison to our theoretical predictions which assumes a perfect
contact of all hairs' terminals.

In the model, we assume that all the hairs detach simultaneously to
give a theoretical maximum achievable adhesion force. In our experiments,
however, not all hairs make a perfect contact with the substrate despite our 
best efforts to align the pad parallel to the surface. Furthermore, during detachment, 
the constrained pad typically peels off from its proximal to distal end rather
than detach simultaneously. Our model also assumes the hairs to be
of similar geometry, unlike the male beetle's pad which has a distribution
of flat or pointed tipped hairs. Thus, it's not surprising that the
model overestimates the adhesion forces. The predictions are however
in the same order of magnitude as experiments, and the qualitative
trend is consistent for both hydrophilic and hydrophobic substrates
in air and underwater.

Our study provides further validation that capillary forces govern the ladybug's adhesion and van der Waals contribution,
if any, must be negligible. Further, the capillary forces can even
enable ladybug attachment underwater depending on the substrate chemistry.
When underwater, without a trapped bubble, the pads adhere strongly
to a hydrophobic substrate, but poorly to a hydrophilic substrate,
even though it shows similarly strong adhesion to both substrates
in air. This effect can be explained by capillary forces and the wetting properties of the fluid. Our
preliminary chemical composition analysis of a beetle's tarsal secretions before and after immersing its leg underwater (unpublished data) suggests that the tarsal adhesive fluid do not get washed away when underwater. Therefore, the fluid should be able to form capillary bridges and help mediate adhesion even when underwater.

To some extent, the findings could be extended to other animals relying on oily
secretions for adhesion. For example, ants are known to possess smooth adhesive pads which secrete a fluid containing oily substances \cite{RN201}.
It has been reported that some ants show similar adhesion on hydrophobic substrates under wet and dry conditions \cite{RN213},
similar to what we see in a ladybug. This observation can again be explained by a capillary model as before. Recent experiments on
geckos revealed that they can attach well to fluoropolymer substrates (such as PTFE)
underwater while they show little adhesion to the same substrate in
air\cite{RN199,RN15}. Geckos are thought to rely on van der Waals
forces via dry contact with the substrate \cite{RN202}, although
recent observations of phospholipid footprints left behind walking
geckos \cite{RN205} could change that picture. Since geckos adhere
poorly to PTFE (surface energy $\sim$ 20 mN m\protect\textsuperscript{-1}) one can
speculate that the phospholipid material has a higher surface energy,
and consequently makes a higher contact angle with PTFE in air. Let
us assume the phosopholipid substance to be a fluid similar to oil 
with $\gamma_{fa}$= 30 mN m\protect\textsuperscript{-1} and $\gamma_{fw}$= 42 mN m\protect\textsuperscript{-1} such that
its contact angle with PTFE is 80\textdegree . Equation \ref{eq:theta_fw}
then gives us an underwater contact angle of 70\textdegree{} for the
phospholipid fluid. Thus, on a PTFE surface, the capillary bridge
model can predict a higher adhesion underwater than in air due to
its lower contact angle and higher interfacial energy underwater.
Based on similar assumptions, we predict the net adhesion force for
the gecko on different substrates (Figure \ref{fig:Comparison-with-model}).
The adhesion force predictions are in good qualitative agreement with
the whole animal experimental shear force values reported for the
gecko, with the trend of higher adhesion in air than underwater for
glass, similar adhesion in air and underwater for PMMA/OTS-SAM and
lower adhesion in air than underwater for PTFE. We, thus, propose
that the underwater experiments performed on geckos \cite{RN199,RN15}
indicate a capillary contribution to gecko adhesion. Previous studies on gecko adhesion have attributed capillary effects to be a result of water monolayers adsorbed from ambient humid air onto the spatuale hair tips \cite{RN197, RN203, RN218}.
We however emphasize that capillary contribution in gecko adhesion could rather be a result of its setal phospholipid layer rather than water.
The previously reported influence of humidity on gecko adhesion \cite{RN197} could possibly be an effect of change in surface tension of the oily phospholipid layer at different humidity, which will in-turn influence the capillary adhesion force. We suggest performing single seta adhesion force tests similar to \citet{RN202}
using a hydrophilic and fluorinated probe in air and underwater conditions. 
If the fluorinated probe shows higher adhesion underwater than in air on a single seta, this
would confirm the role of capillary contributions due to an oil-like phospholipid layer to gecko adhesion. Further work is also necessary to validate if the phospholipid layer in geckos' toes indeed has fluid-like properties.

### 2021-05-10 source/tex/supplementary.tex
finalized manuscript based on thomas's suggestions
ready to send to JEB

\title{Wetting of the adhesive fluid controls underwater adhesion in insects: Supplementary material}

@@

Pairwise statistical comparison of single leg adhesion force measurements
of the ladybug beetle (\emph{Coccinella septempuctata}) for each contact
type and substrate are shown (Table \ref{tab:Statistical-analysis}).
The uncorrected p-values and Common Language Effect Size (CLES) are
obtained from post-hoc pair-wise Student t-test between A and B while
keeping the third parameter fixed. p-values showing statistically
significant difference between A and B are in boldface. The condition
for statistical significance is based on the Bonferroni-corrected
critical p-value of 0.008.

\begin{table}[H]
\noindent \begin{centering}
\begin{tabular}{|>{\raggedright}m{0.15\linewidth}|>{\raggedright}m{0.15\linewidth}|>{\raggedright}m{0.15\linewidth}|>{\centering}m{0.15\linewidth}|>{\centering}m{0.15\linewidth}|}
\hline 
Fixed & A & B & p-value & CLES\tabularnewline
\hline 
\hline 
In air & PFOTS & Glass & 0.959 & 0.48\tabularnewline
\hline 
Underwater: bubble & PFOTS & Glass & 0.011 & 0.96\tabularnewline
\hline 
Underwater: no bubble & PFOTS & Glass & \textbf{< 0.001} & 1.0\tabularnewline
\hline 
PFOTS & In air & Underwater: bubble & 0.897 & 0.48\tabularnewline
\hline 
PFOTS & In air & Underwater: no bubble & 0.828 & 0.48\tabularnewline
\hline 
PFOTS & Underwater: bubble & Underwater: no bubble & 0.721 & 0.44\tabularnewline
\hline 
Glass & In air & Underwater: bubble & \textbf{0.002} & 1.0\tabularnewline
\hline 
Glass & In air & Underwater: no bubble & \textbf{< 0.001} & 1.0\tabularnewline
\hline 
Glass & Underwater: bubble & Underwater: no bubble & 0.07 & 0.84\tabularnewline
\hline 
\end{tabular}
\par\end{centering}
\caption{\label{tab:Statistical-analysis}}
\end{table}

@@

Capillary force of a single bubble against a PFOTS surface are compared
for two different volumes. The volumes correspond to the expected
range in the case of the trapped bubble in a ladybug. Here, the bubble
is pinned to a micropatterned PDMS substrate on the top. The maximum
adhesion force of any of the bubble never exceeds 50 \textmu N,
significantly lower than the beetle's underwater adhesion to the same
substrate (> 400 \textmu N). Thus, the bubble's contribution
to adhesion in the ``\emph{underwater: bubble}'' contact of a ladybug's
pad should be negligible.

>>>>

\title{Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles: Supplementary information (S1)}

@@

Two-way ANOVA test showed a significant effect of the \emph{Contact mode} (p=0.001, F=9.596, degrees of freedom=2) 
and \emph{Substrate} (p<0.001, F=36.231, degrees of freedom=1) categories on the single leg adhesion force measurements
of the ladybug beetle (\emph{Coccinella septempuctata}). Signifanct interaction between the above two was seen (p=0.001, F=10.551, degrees of freedom=2). Post-hoc analysis results are shown below (Table \ref{tab:Statistical-analysis}).
The uncorrected p-values and Common Language Effect Size (CLES) are
obtained from pair-wise Student t-test between A and B while
keeping the third parameter fixed. p-values showing statistically
significant difference between A and B are in boldface. 
CLES represents the statistical proportion of samples under A with higher adhesion than under B. The condition
for statistical significance is based on the Bonferroni-corrected
critical p-value of 0.008.

\begin{table}[H]
\noindent \begin{centering}
\begin{tabular}{|>{\raggedright}m{0.15\linewidth}|>{\raggedright}m{0.15\linewidth}|>{\raggedright}m{0.15\linewidth}||>{\centering}m{0.1\linewidth}|>{\centering}m{0.1\linewidth}|>{\centering}m{0.1\linewidth}|}
\hline
Fixed variable & A & B & T & p-value & CLES\tabularnewline
\hline 
\hline 
In air & PFOTS & Glass & -0.053 & 0.959 & 0.48\tabularnewline
\hline
Underwater: bubble & PFOTS & Glass & 3.292 & 0.011 & 0.96\tabularnewline
\hline
Underwater: no bubble & PFOTS & Glass & 10.044 & 0.0 & 1.0\tabularnewline
\hline
PFOTS & In air & Underwater: bubble & 0.133 & 0.897 & 0.48\tabularnewline
\hline
PFOTS & In air & Underwater: no bubble & -0.224 & 0.828 & 0.48\tabularnewline
\hline
PFOTS & Underwater: bubble & Underwater: no bubble & -0.37 & 0.721 & 0.44\tabularnewline
\hline
Glass & In air & Underwater: bubble & 4.688 & 0.002 & 1.0\tabularnewline
\hline
Glass & In air & Underwater: no bubble & 11.341 & 0.0 & 1.0\tabularnewline
\hline
Glass & Underwater: bubble & Underwater: no bubble & 2.086 & 0.07 & 0.84\tabularnewline
\hline 
\end{tabular}
\par\end{centering}
\caption{\label{tab:Statistical-analysis}}
\end{table}

@@

Capillary force of a single bubble against a PFOTS surface are compared
for two different volumes. The volumes correspond to the expected
range in the case of the trapped bubble in a ladybug. Here, the bubble
is pinned to a micropatterned PDMS substrate on the top. The maximum
adhesion force of any of the bubble never exceeds 50 \textmu N,
significantly lower than the beetle's underwater adhesion to the same
substrate (> 400 \textmu N). Thus, the bubble's contribution
to adhesion in the ``\emph{underwater: bubble}'' contact of a ladybug's
pad should be negligible. Example measurement video is included in the supplementary data (S4).
